---
title: "Lazy_learning_Classification_using_nearest_neighbors"
output: html_document
---

---
The kNN Algo
1) Class: benign and malignant
2) Calculate the distance between target and nearest k neighbors. Find the shortest distance to decide target's class
3) Too large k may cause the target being classified into the class which has most common characteristic. Too small k may cause overfitted (the target may have singularity and be misclassified)
---
```{r}
download.file('https://archive.ics.uci.edu/ml/machine-learning-databases/breast-cancer-wisconsin/breast-cancer-wisconsin.data',destfile = '/Users/yisongdong/Desktop/MSF&Python/MSF/Big Data Analysis/machine_learning/Breast Cancer Wisconsin Diagnostic/cancer.csv')
download.file('https://archive.ics.uci.edu/ml/machine-learning-databases/breast-cancer-wisconsin/breast-cancer-wisconsin.names',destfile = '/Users/yisongdong/Desktop/MSF&Python/MSF/Big Data Analysis/machine_learning/Breast Cancer Wisconsin Diagnostic/cancer_name.txt')
download.file('https://archive.ics.uci.edu/ml/machine-learning-databases/breast-cancer-wisconsin/wdbc.data',destfile = '/Users/yisongdong/Desktop/MSF&Python/MSF/Big Data Analysis/machine_learning/Breast Cancer Wisconsin Diagnostic/wbcd.csv')
```
```{r}
wbcd_data<-read.csv('/Users/yisongdong/Desktop/MSF&Python/MSF/Big Data Analysis/machine_learning/Breast Cancer Wisconsin Diagnostic/wbcd.csv',header = FALSE, stringsAsFactors = FALSE)
colnames(wbcd_data)<-c('Id','Diagnosis','radius_mean','?','?','area_mean','smoothness_mean')
```

```{r}
table(wbcd_data$Diagnosis)
```
```{r}
# Many R machine learning classi ers require that the target feature is coded as a factor, so we will need to recode the diagnosis variable. We will also take this opportunity to give the B and M values more informative labels using the labels parameter:
wbcd_data$Diagnosis<-factor(wbcd_data$Diagnosis, levels=c('B','M'), labels = c('Benign', 'Malignant'))
table(wbcd_data$Diagnosis)
```
```{r}
prop.table(table(wbcd_data$Diagnosis))*100
```
```{r}
summary(wbcd_data[c('radius_mean','area_mean','smoothness_mean')])
```

Transformation--normalizing numerica data
```{r}
# scale all values
normalize1<-function(x){
  return((x-min(x))/(max(x)-min(x)))
}
```
```{r}
wbcd_scaled1<-as.data.frame(lapply(wbcd_data[3:32], normalize1))
summary(wbcd_scaled1[c('radius_mean','area_mean','smoothness_mean')])
wbcd_scaled1
```
```{r}
# don't re-run this chunk, or the order will be a mess.
# if have to re-run, then run last chunk first.
require(dplyr)
wbcd_scaled1<-mutate(wbcd_scaled1, Diagnosis = wbcd_data$Diagnosis)
wbcd_scaled1<-wbcd_scaled1[,c(31,1:30)]
wbcd_scaled1
```


Data Preparation--creating training and test datasets
```{r}
# randomly choose 469 training data and 100 test data
set.seed(11)
train_id<-sample(569,469)
```
```{r}
# reserve training set & testing set in different dataframe
wbcd_train<-wbcd_scaled1[train_id,c(1,2,5,6)]
wbcd_test<-wbcd_scaled1[-train_id,c(1,2,5,6)]
```

Training a model on the data
```{r}
# need to load a package called class
if(!require(class)){
  install.packages('class')
}
```
```{r}
# Class package has knn() function, which provides a standard and classic inplementation of kNN algorithm. knn() function performed in a single function call, using 4 parameters, as shown in knn(train, test, cl, k).
# ** parameter 'cl' (class) is a factor vector with the class for each row in training data
# more sophiscated kNN functions can refer to CRAN
wbcd_knn<-knn(train = wbcd_train[,2:4], test = wbcd_test[,2:4], cl = wbcd_train$Diagnosis, k=11)
wbcd_knn
# WARNING: when use knn() function, 'train' and 'test' can't include the 'class' vector, therefore we choose 'train = wbcd_train[,2:4], test = wbcd_test[,2:4]'. 
```

Evaluating model performance
```{r}
# compare the evaluating result and test data set
# we don't need chi square here
require(gmodels)
CrossTable(x = wbcd_knn, y = wbcd_test$Diagnosis, prop.chisq  = FALSE)
```
The upper left cell and lower right cell of the cross table indicates kNN correctly evaluate the result (evaluate bening as benign and malignant as malignant) . Upper right and lower left means misvalued (evaluate malignant as benign and benign as malignant).


Improving model performance
```{r}
# First improvement: rescaling numeric features with z-score method
summary(wbcd_data[,c(3,6,7)])

# this function does the z-score scaling
normalize2<-function(x){
  return((x-mean(x))/sd(x))
}
```
```{r}
wbcd_scaled2<-as.data.frame(lapply(wbcd_data[,c(3,6,7)],normalize2))
wbcd_scaled2<-mutate(wbcd_scaled2,Diagnosis=wbcd_data$Diagnosis)
wbcd_scaled2<-wbcd_scaled2[,c(4,1:3)]
wbcd_scaled2
```
```{r}
set.seed(22)
train<-sample(569,469)
wbcd_z_score_train<-wbcd_scaled2[train,]
wbcd_z_score_test<-wbcd_scaled2[-train,]
```
```{r}
wbcd_z_score_train
wbcd_z_score_test
```
```{r}
kNN_result2<-knn(train = wbcd_z_score_train[,2:4], test = wbcd_z_score_test[,2:4], cl = wbcd_z_score_train$Diagnosis, k=11)
kNN_result2
```
```{r}
CrossTable(x = kNN_result2, y = wbcd_z_score_test$Diagnosis, prop.chisq = FALSE)
```
```{r}
# Second improvement: testing alternative values of k
```













